\Title

### 2022-09-27 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.1

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
Machine learning, and computer vision in particular, have seen a sharp transition in modern times from moving from science fiction movies to a mainstream status, present in the smartphones that sit in each and everybody's pocket. Less visible but even more important to our economy and security, numerous automated tools are now prominent in the services that empowers essentially all sectors of our daily life. This is most acute in medicine for which it empowers practionners with novel diagnostic tools to heal people sooner and better. This particular example illustrates also some important challenges increasingly faced by these tools. One of these is their sensibility to adversarial attacks, that is the sensibility of the models' output to minute changes in the input. This Could raise important issues on the reliability about the results any automated diagnostic model. More generally, these models lack also to offer why it forms a given output for a class of inputs. This lack of explainability hinders the general advances and acceptance of these methods for most secure-sensitive tasks.

Taking some perspective, one remembers that these tools are inherited by theoretical models made to understand the brain. While the first artificial neural network were mainly applied on toy-like problems, they were also offering a growing number of applications in computer vision but also more generally for automating tasks. In particular, convolutional neural networks are inspired by the feed-forward processing observed in the visual pathways of primates and reaches now super-human performances for categorizing images. One challenge with these models is to be able to scale them up for prospective applications, for instance in autonomous driving. Indeed, in such applications, the input does not consist of a single image (let's say of about a few million pixels) but of a continuous stream of images from multiple cameras.

Challenges are numerous in that case and we should put forward two major hurdls: rapidity and energy budget. First, most existing solutions are being built incrementally from low-definition images such as Le Net for MNIST (Le Cun, 98), to high definition images, such as VGG on Imagenet (VGG16). This comes at a cost and notably that the computation time increases with image size. This has been tampered by the increase of computational power available, notably with the parallel processing implemented in GPU cards. However, transitioning from images to videos, and then to multiple cameras involves a change of scale in the amount of data processed. It raises also a question which is often of little importance when dealing with image categorization. Indeed, in the setting of autonomous driving, an important task is to respond as fast as possible to an eventual collision, for instance as a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait until the pipeline delivers the correct response. This online processing is also a hallmark of processing in biological systems. This could be a first important contribution if we could translate these principles into future automated processes.

>>>>

%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
\label{sec:intro}
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
%
\subsection{Recent challenges in machine learning and computer vision}
%%%-----------------------------------------------------------------
Machine learning, and computer vision in particular, have undergone a major transformation in modern times, leaving science fiction movies to become mainstream tools found in the smartphones in everyone's pocket. Less visible, but even more crucial to our economy and security, are the many automated tools that now dominate the range of services that equip virtually all sectors of our daily lives. This trend is most pronounced in the field of medicine, as it provides practitioners with new diagnostic tools to treat people faster and more effectively. This particular example also illustrates some important challenges that these tools are increasingly facing. One of these is their sensitivity to adversarial attacks, that is, the sensitivity of the models' output to minute changes in the input. This could raise important questions about the reliability of the results of in any automated diagnostic model. More generally, these models do not explain why they produce a given output for a class of inputs. This lack of explainability is a hindrance to the advancement of these methodologies as well as to their acceptance for most safety-relevant tasks.

If we take a step back, we will remember that these tools are inherited from theoretical models designed to understand the brain. While the first artificial neural networks were mainly applied to " toy " type problems, they also offered a growing number of applications in computer vision, but also more generally for task automation. In particular, convolutional neural networks are inspired by the feed-forward processing observed in the visual pathways of primates, and today they reach higher performances than humans for image categorization. One of the challenges of these models is to be able to scale them up for future applications, for example in autonomous driving. Indeed, in such applications, the input does not consist of a single image (say a few million pixels) but of a continuous stream of images from several cameras.

The challenges are numerous in such situations and two major obstacles must be highlighted: the computational delay and the energy budget. First, most existing solutions are built incrementally from models built to process low definition images, such as Le Net for MNIST (Le Cun, 98), to high definition images, such as VGG on Imagenet (VGG16). This has a cost and notably the fact that the computation time increases with the size of the image. This phenomenon has been mitigated by the increase in available computing power, notably thanks to the parallel processing implemented in GPU cards. However, the transition from images to videos, then to multiple cameras implies a further change of scale in the amount of data processed. It also raises an issue that is often not addressed when it comes to image categorization. Indeed, in autonomous driving, an important task is to react as quickly as possible to a possible collision, for example when a pedestrian crosses the street. As such, future systems should always be able to give a response at any time, instead of having to wait for the pipeline to provide the correct response. This online processing is also a feature of processing in biological systems and could be an important first contribution if we could translate these principles into future automated processes.
